---
title: "Repairing Dallas Report Insights"
---

```{r, Load Data}
#| include: FALSE
#| 
#####  Load Libraries #####
library(tidycensus)
library(tidyverse)
library(rio)
library(sf)
library(cpaltemplates)
library(plotly)
library(DT)

#datalib <- "E:/CPAL Dropbox/" # Michael Desktop Directory
datalib <- "C:/Users/Michael/CPAL Dropbox/" # Michael Laptop Directory

repair <- rio::import("data/Repairing Dallas Survey Responses - Geocode.csv") %>%
    mutate(flag_u18 = ifelse(tot_u18 > 0, TRUE, FALSE))

# function to calculate percentages against two groups
calculate_percentages <- function(data, group_col1, group_col2) {
  result <- data %>%
    filter(!is.na({{group_col1}})) %>%
    group_by({{group_col1}}, {{group_col2}}) %>%
    summarize(count = n()) %>%
    group_by({{group_col2}}) %>%
    mutate(percent = count / sum(count))
  
  all_responses <- data %>%
    filter(!is.na({{group_col1}})) %>%
    group_by({{group_col1}}) %>%
    summarize(count = n()) %>%
    mutate(percent = count / sum(count),
           {{ group_col2 }} := "All Responses")
  
  result <- bind_rows(result, all_responses)
  
  return(result)
}

repairSummer <- repair %>%
  select(race, tempsummer) %>%
  separate(tempsummer, into = c("item1", "item2", "item3", "item4", "item5", "item6"), sep = ",", fill = "right") %>%
  pivot_longer(cols = item1:item6, values_to = "tempsummer") %>%
  filter(!is.na(tempsummer)) %>%
  select(-name) %>%
  mutate(tempsummer = case_when(tempsummer == "A central air conditioning unit (Una unidad central de aire acondicionado.)" ~ "Central A/C",
                                tempsummer == "Box fans/fans that are plugged in (Ventiladores de caja/ventiladores que están enchufados.)" ~ "Box Fans",
                                tempsummer == " A central air conditioning unit (Una unidad central de aire acondicionado.)" ~ "Central A/C",
                                tempsummer == "" ~ "No Response",
                                tempsummer == " Window air conditioning unit(s) (Unidad(es) de aire acondicionado de ventana.)" ~ "Window A/C",
                                tempsummer == " Ceiling fans (Ventiladores de techo.)" ~ "Ceiling Fans",
                                tempsummer == " Box fans/fans that are plugged in (Ventiladores de caja/ventiladores que están enchufados.)" ~ "Box Fans",
                                tempsummer == " Opening windows (Abriendo las ventanas.)" ~ "Opening Windows",
                                tempsummer == "Opening windows (Abriendo las ventanas.)" ~ "Opening Windows",
                                tempsummer == "Window air conditioning unit(s) (Unidad(es) de aire acondicionado de ventana.)" ~ "Window A/C",
                                tempsummer == "Ceiling fans (Ventiladores de techo.)" ~ "Ceiling Fans",
                                tempsummer == "E" ~ "No Response"
                                ))

repairWinter <- repair %>%
  select(race, tempwinter) %>%
  separate(tempwinter, into = c("item1", "item2", "item3", "item4", "item5", "item6"), sep = ",", fill = "right") %>%
  pivot_longer(cols = item1:item6, values_to = "tempwinter") %>%
  filter(!is.na(tempwinter)) %>%
  select(-name) %>%
  mutate(tempwinter = case_when(tempwinter == "A central heating unit (Una unidad de calefacción central.)" ~ "Central Heat",
                                tempwinter == " A central heating unit (Una unidad de calefacción central.)" ~ "Central Heat",
                                tempwinter == "Space heaters (Calentadores de espacio.)" ~ "Space Heaters",
                                tempwinter == " Space heaters (Calentadores de espacio.)" ~ "Space Heaters",
                                tempwinter == " Towel on doors" ~ "Towel on Doors",
                                tempwinter == "Towel on doors" ~ "Towel on Doors",
                                tempwinter == " Radiators (Radiadores.)" ~ "Radiators",
                                tempwinter == "Radiators (Radiadores.)" ~ "Radiators",
                                tempwinter == "Stove" ~ "Kitchen Stove",
                                tempwinter == "Wood Stove" ~ "Kitchen Stove",
                                tempwinter == "Furnace and stove" ~ "Kitchen Stove",
                                tempwinter == "My kitchen stove" ~ "Kitchen Stove",
                                tempwinter == "Calentador de gas" ~ "Gas Heater",
                                tempwinter == "Gas geater" ~ "Gas Heater",
                                tempwinter == "Radiators (Radiadores.)" ~ "Radiator",
                                tempwinter == "Fireplace (Chimenea.)" ~ "Fireplace",
                                tempwinter == "None" ~ "Nothing",
                                tempwinter == " By" ~ ""
                                )) %>%
  filter(tempwinter != "") %>%
  filter(!is.na(tempwinter))
```

#### Question Summaries and Breakdowns

This document is intended to breakdown all Repairing Dallas questions by overall responses and breakdowns by Race/Ethnicity.

White Non-Hispanic, Hispanic or Latino, and Black or African American are the main groups being shown on these images, because other groups only accounted for a total of 5 responses and were thusly excluded.

Numbers generated in this are intended to be used in a Repairing Dallas report.

## Survey Responses by Demographics

```{r, Households by Poverty}
question1 <- calculate_percentages(data = repair, group_col1 = incomethreshold, group_col2 = race) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  mutate(group = case_when(
    is.na(incomethreshold) ~ "No Response",
    incomethreshold == TRUE ~ "Household Below FPL",
    incomethreshold == FALSE ~ "Household Above FPL")) %>%
  mutate(group = factor(group, levels = c("Household Below FPL", "Household Above FPL", "No Response"))) %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
  guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Households Above or Below the Federal Poverty Line",
                     width = 75),
          question1, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Children}
question2 <- calculate_percentages(data = repair, group_col1 = flag_u18, group_col2 = race) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  mutate(group = case_when(
    is.na(flag_u18) ~ "No Response",
    flag_u18 == TRUE ~ "Yes",
    flag_u18 == FALSE ~ "No")) %>%
#  mutate(group = factor(group, levels = c("Household Below FPL", "Household Above FPL", "No Response"))) %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Households with Children",
                     width = 75),
          question2, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Over 65}
question11 <- calculate_percentages(data = repair, group_col1 = over65, group_col2 = race) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  mutate(group = case_when(
    is.na(over65) ~ "No Response",
    over65 == TRUE ~ "Over 65 in Home",
    over65 == FALSE ~ "No Over 65 in Home")) %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
  guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Households with Elderly (Over 65) in Home",
                     width = 75),
          question11, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Under 6}
question12 <- calculate_percentages(data = repair, group_col1 = frequent_u6, group_col2 = race) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  mutate(group = case_when(
    is.na(frequent_u6) ~ "No Response",
    frequent_u6 == TRUE ~ "Under 6 in Home",
    frequent_u6 == FALSE ~ "No Under 6 in Home")) %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
  guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Households with Young Child (Under 6) in Home",
                     width = 75),
          question12, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

## Survey Responses by Safety Items

```{r, Households by CO Detector}
question3 <- repair %>%
  select(safety_carbonmono, race) %>%
  mutate(group = case_when(safety_carbonmono == "Yes (Si.)" ~ "Yes",
                           safety_carbonmono == "No (No.)" ~ "No",
                           safety_carbonmono == "Unsure (No estoy seguro.)" ~ "Unsure", 
                           safety_carbonmono == "" ~ "No Response")) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
#  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Carbon Monoxide Detector in Home",
                     width = 75),
          question3, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Fire Extinguisher}
question4 <- repair %>%
  mutate(group = ifelse(safety_extinguisher == "Yes (Si.)", "Yes",
                        ifelse(safety_extinguisher == "No (No.)", "No",
                               ifelse(safety_extinguisher == "Unsure (No estoy seguro.)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Fire Extinguisher in Home",
                     width = 75),
          question4, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Smoke Detector}
question5 <- repair %>%
  mutate(group = ifelse(safety_smoke == "Yes (Si)", "Yes",
                        ifelse(safety_smoke == "No (No)", "No",
                               ifelse(safety_smoke == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Smoke Detector in Home",
                     width = 75),
          question5, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Air Filter}
question17 <- repair %>%
  mutate(group = case_when(
    is.na(airfilter) ~ "No Response",
    airfilter == TRUE ~ "Yes",
    airfilter == FALSE ~ "No")) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Do you change your air filter?",
                     width = 75),
          question17, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

## Survey Responses by Home Status
```{r, Households by Home Status}
question6 <- calculate_percentages(data = repair, group_col1 = home_status, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  mutate(group = ifelse(str_detect(home_status, "Rented by you"), "Rented by Occupant",
                        ifelse(str_detect(home_status, "Owned by you or someone in this household with a mortgage or loan"), "Owned, but not Paid Off",
                               ifelse(str_detect(home_status, "Owned by you or someone in this household free and clear"), "Owned and Paid Off", "ERROR")))) %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "What is the status of your home?",
                     width = 75),
          question6, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Temperature Control in Summer}
question9 <- repairSummer %>%
  calculate_percentages(group_col1 = tempsummer, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = tempsummer)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = ifelse(percent >= 0.05, paste0(round(percent*100, digits = 0), "%"), "")),
            position = position_stack(vjust = 0.5),
            color = palette_cpal_main[3],
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_orange) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Temperature Control in Summer",
                     width = 75),
          question9, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Temperature Control in Winter}
question10 <- repairWinter %>%
  calculate_percentages(group_col1 = tempwinter, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = tempwinter)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = ifelse(percent >= 0.05, paste0(round(percent*100, digits = 0), "%"), "")),
            position = position_stack(vjust = 0.5),
            color = palette_cpal_main[3],
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_teal) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Temperature Control in Winter",
                     width = 75),
          question10, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

## Survey Responses by Owner-Occupied Homes

```{r, Households by Owners Insurance}
question8 <- repair %>%
  filter(str_detect(home_status, "Owned by you")) %>%
  mutate(group = ifelse(home_insurance == "Yes (Si)", "Yes",
                        ifelse(home_insurance == "No (No)", "No",
                               ifelse(home_insurance == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Do you have renters insurance?",
                     width = 75),
          question8, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Home Title}
question13 <- repair %>%
  filter(str_detect(home_status, "Owned by you")) %>%
  mutate(group = ifelse(home_title == "Yes (Si)", "Yes",
                        ifelse(home_title == "No (No)", "No",
                               ifelse(home_title == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Do you have your homes title?",
                     width = 75),
          question13, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Home Built Before 1979}
question14 <- repair %>%
  filter(str_detect(home_status, "Owned by you")) %>%
  mutate(group = ifelse(home_1979 == "Yes (Si)", "Yes",
                        ifelse(home_1979 == "No (No)", "No",
                               ifelse(home_1979 == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Home Built Before 1979",
                     width = 75),
          question14, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Homestead Exemption}
question15 <- repair %>%
  filter(str_detect(home_status, "Owned by you")) %>%
  mutate(group = ifelse(homesteadexempt == "Yes (Si)", "Yes",
                        ifelse(homesteadexempt == "No (No)", "No",
                               ifelse(homesteadexempt == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
    guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Homestead Exemption on Home",
                     width = 75),
          question15, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

## Survey Responses by Renter-Occupied Homes

```{r, Households by Renters Insurance}
question7 <- repair %>%
  filter(str_detect(home_status, "Rented by you")) %>%
  mutate(group = ifelse(rent_insurance == "Yes (Si.)", "Yes",
                        ifelse(rent_insurance == "No (No)", "No",
                               ifelse(rent_insurance == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
  guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Do you have renters insurance?",
                     width = 75),
          question7, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```

```{r, Households by Rent Lease}
question16 <- repair %>%
  filter(str_detect(home_status, "Rented by you")) %>%
  mutate(group = ifelse(rent_lease == "Yes (Si)", "Yes",
                        ifelse(rent_lease == "No (No)", "No",
                               ifelse(rent_lease == "Unsure (No estoy seguro)", "Unsure", "No Response")))) %>%
  filter(group != "No Response") %>%
  calculate_percentages(group_col1 = group, group_col2 = race) %>%
  ungroup(.) %>%
  mutate(race = factor(race, levels = c("All Responses", 
                                        "Black or African American",
                                        "Hispanic or Latino",
                                        "White Non-Hispanic",
                                        "Other",
                                        "No Response"))) %>%
  filter(race != "Other") %>%
  ggplot(aes(x = percent, y = fct_rev(as_factor(race)), fill = group)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  geom_text(aes(label = paste0(round(percent*100, digits = 0), "%")),
            position = position_stack(vjust = 0.5),
            color = "#FFFFFF",
            fontface = "bold") +
  scale_fill_manual(values = palette_cpal_main) +
  labs(x = "",
       y = "") +
  theme_cpal_print() +
  remove_axis(axis = "x") +
  remove_ticks() +
  guides(fill = guide_legend(reverse = TRUE))

cpal_plot(zeroGrob(),
          cpal_title(string = "Current Rental Lease on Home",
                     width = 75),
          question16, 
          zeroGrob(),
          cpal_logo_text(), 
          ncol = 1,
          heights = c(1, 3, 30, 1, 2))

```