---
title: "Repairing Dallas Report Insights"
format: html
editor: visual
---

```{r}
#| echo: false
library(tidyverse)
library(sf)
library(rio)

libDB <- "C:/Users/Michael/CPAL Dropbox/"

repairPivot <- rio::import(paste0(libDB, "Housing/04_Projects/Repairing Dallas/Data/Repairing Dallas Survey Responses - Geocode.csv"))

```

## Question Summaries and Breakdowns

This document is intended to breakdown all Repairing Dallas questions by overall responses and breakdowns by Race/Ethnicity or Children in Home.

Numbers generated in this are intended to be used in a Repairing Dallas report.

#### Survey Responses Above/Below Federal Poverty Line

```{r}
#| echo: false
repairPivot %>%
  group_by(incomethreshold) %>%
  summarize(count = n()) %>%
  mutate(percent = scales::percent(count/sum(count), accuracy = 0.1)) %>%
  mutate(incomethreshold = ifelse(incomethreshold == TRUE, "Household Below FPL", "Household Above FPL"))
```

#### Above/Below Federal Poverty Line by Race/Ethnicity
```{r}
#| echo: false

repairPivot %>%
  group_by(incomethreshold, race) %>%
  summarize(count = n()) %>%
  mutate(incomethreshold = ifelse(incomethreshold == TRUE, "Below FPL", "Above FPL")) %>%
  pivot_wider(names_from = incomethreshold, values_from = count, values_fill = 0)
```
#### Above/Below Federal Poverty Line by Children in Home
```{r}
#| echo: false

repairPivot %>%
  mutate(children = ifelse(tot_u18 > 0, "No Children", "Children")) %>%
  group_by(incomethreshold, children) %>%
  summarize(count = n()) %>%
  mutate(incomethreshold = ifelse(incomethreshold == TRUE, "Below FPL", "Above FPL")) %>%
  pivot_wider(names_from = incomethreshold, values_from = count, values_fill = 0)
```

